Poseidon Adventure

### 2019-06-04 docs/index.Rmd
add initial sardines with new CCA
update full example
fix what I broke

@@

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/SardinesOnlyatlantisom2SStest.html" target="_blank">Start on Sardines in the CalCurrent, all true and SS data, May 31, 2019, updated June 3</a>

@@

### Rabbit holes that turned out ok

<a href="https://sgaichas.github.io/poseidon-dev/CheckBiomassAges.html" target="_blank">In which I broke the very first thing that worked, then fixed it - June 4, 2019</a>
